Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments

### 2020-11-16 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.fix some typo mistakes for x.

  Image classification and categorization are essential to the capability of telling the difference between images for a machine
  which is initially designed for vision purposes.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

@@

\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands news reports in 10 domains.

\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
The \textit{Two-Case} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Four-Case} dataset has $34789$ training documents and $2013$ test documents.

\par From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
the test accuracy exceeds the other popular machine learning algorithms.
Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.

@@

\par The CIFAR-10 dataset contains 60000 color images with a resolution of $32\times32$ in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other meta-data if provided, as a sequence of ASCII characters.
In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of the BERT language model, a sequence larger than $512$ needs to be trimmed before sending it to the BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
In the Output layer, the classification label of the image is feed in the model.

@@

Using the proposed model, I tried different pre-trained language models to see the impact on classification accuracy.
From the Table (2), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
however, its training cost grows for the larger language model.
For the same fine-tuned language model, classes number has positive impact on the accuracy,
the fewer classes the dataset has, the more accurate results the model can achieve.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 6	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
\hline
RBT3   & CIFAR-100 & 12	&	99.66\% \\
RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large.}
\end{table}

@@

 Compare to iGPT-L's accuracy of 96.3\% on the CIFAR-10 dataset without augmentation and 82.8\% on the CIFAR-100 dataset, our models have preferable better results.
The reason that the model's outstanding performance lies in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use of extra language corpus of
$5.4$ billions of tokens of wiki data and other resources.
The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, \eg object detection, gesture prediction.

@@

 This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
 The finding might benefit various subjects, namely Education, Medical, Chemistry, Physics, Cosmology, Geography, Climate and Materials Science for their specific research.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

>>>>

  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
  As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

@@

Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands news reports in 10 domains.

I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
The \textit{Two-Case} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Four-Case} dataset has $34789$ training documents and $2013$ test documents.

From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
the test accuracy exceeds the other popular machine learning algorithms.
Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.

@@

\par The CIFAR-10 dataset contains 60,000 color images with a resolution of $32\times32$ in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other meta-data if provided, as a sequence of ASCII characters.
In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of the BERT language model, a sequence larger than $512$ needs to be trimmed before sending it to the BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as Equation (2), is used.
In the Output layer, the classification label of the image is feed in the model.

@@

Using the proposed model, I tried different pre-trained language models to see the impact on classification accuracy.
From the Table (2), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
however, its training cost grows for the larger language model.
For the same fine-tuned language model, classes number has positive impact on the accuracy.
And the fewer classes the dataset has, the more accurate results the model can achieve.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Language Model 	& Dataset & Epoch & Accuracy \\
\hline\hline
RBT3   & CIFAR-10 & 6	&	99.74\% \\
RBTL3  & CIFAR-10 & 6	&	99.72\% \\
RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
\hline
RBT3   & CIFAR-100 & 12	&	99.66\% \\
RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
\hline\hline
iGPT-L & CIFAR-10 & $18_a$ & 99.0\%\\
iGPT-L & CIFAR-100 & $18_a$ & 88.5\%\\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models and iGPT-L on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
RoBERTa-large is short for RoBERTa-wwm-ext-large. (a) iGPT-L model was trained far more than 18 epochs, it was trained by 1,000,000 iterations of pre-training and a few epochs for fine-tuning.}
\end{table}

@@

The iGPT-L was trained on the ImageNet dataset, and it has 48 layers of transoformers and 1.4 billion parameters, and the embedding size takes 1536,
so it has almost identical layers with GPT-2 language model, except for 1.5 billion parameters and 1600 embedding size.
Compare to iGPT-L's accuracy of 96.3\% on the CIFAR-10 dataset without augmentation and 82.8\% on the CIFAR-100 dataset, our models have preferable better results.
The reason that the model's outstanding performance lies in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use of extra language corpus of
$5.4$ billions of tokens of wiki data and other resources.
The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, \eg object detection, gesture prediction.

@@

 This paper proposed a novel idea by using the pre-trained language models for image representation and take image classification
 as an example to prove its performance for Computer Vision tasks, such as image classification.
 The finding might benefit various subjects, namely  for their specific research.
Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

### 2020-11-16 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.fix some typo mistakes for x.

  In the film industry, visualizing actor stars' social media to analyze audience intention towards movies is essential for the movie producers.
  However, non-Euclidean social media are hard to analyze,
  I propose an FC-GRU-CNN architecture, named as \underline{N}on\underline{E}uclidean\underline{N}et, for the social media visualization.
  On the analysis of social media, social relationship representations, network characteristics and media sentiments are the key factors.
  The FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in the long sequences of film cast,
  the mapping ability of the convolutional neural network layer in retrieving all-pairs shortest path of the actors' social relationship,
  and non-linear capability in deep fully connected layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Reed \etal~\cite{reed2016learning}'s model.

@@

  With the development of social networks, the actors' influence in social media is increasing,
  and the influence of actors' consumption spreads through social networks,
  and using the long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between the box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of the movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to summarize the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Reed \etal~\cite{reed2016learning}'s model.

@@

Look at the box-office distribution of $1296$ films released between 2011 and 2015,
the box-office forecasts can be seen as a binary classification task.
To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
So for the movies with less than $2.635$ million box-office are classified as A-class, movies with more than $2.635$ million box-office are classified as B-class.
In the dataset division, the data were randomly selected using the $80\%:20\%$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
Using the actors' social network representation, the actor is quantified, that is,
the fusion of social network features, the shortest path characteristics, and the actors' artistic characteristics.
For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
As shown in Figure 1, the model is divided into three parts:

\begin{itemize}
\item The first part is the fully connected layer, its input feature is the film metadata and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
\item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and artistic characteristics, the film cast is a long list,
the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
\item The last part is the 5 CNN layers, input from the actors' social network shortest path feature, similarly, the film cast is a long list,
input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimension feature extraction.
\end{itemize}
Finally, these three parts are merged into one layer and then connect to a Softmax layer, and the $L_2$ regularization method is adopted to avoid overfitting.

In summary, randomly choose 10 movies as the test set, as shown in Table 1.
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Reed \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
and in the box-office prediction task, the model can provide more accurate predictions in the market.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Movie& Score &BoxOffice\\
\hline\hline
72 hours of sword theft & 1 & 108 \\
Ballera's Little Magic Fairy& 1 & 1916\\
It's us. &1& 28\\
Twin Spirits &1& 310\\
The dinner is crazy too& 1& 4381\\
Basement Horror& 0& 704\\
Tartar Oil Flower Romance& 0& 1\\
Breaking five& 0& 1\\
Kidnapping the door dog& 1& 1\\
Beijing Love Story& 1& 40555\\
\hline
\end{tabular}
\end{center}
\caption{box-office model predictions in movie test dataset with 10 samples.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Reed \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on the prediction models.}
\end{table}

@@

According to the box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN box-office prediction model, tested on a dataset with $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.

>>>>

  In the film industry, visualizing actor stars' social media to analyze audience intention towards movies is essential for the movie producers.
  However, non-Euclidean social media are hard to analyze,
  In the analysis of social media task, social relationship representations, network characteristics and media sentiments are three key factors.
  Thus, I propose an FC-GRU-CNN architecture from the key visualization factors,
  also named as \underline{N}on \underline{E}uclidean \underline{N}et, for the social media visualization.
  The proposed architecture exploits the long-term memory ability of the GRU layers in the long sequences of film cast,
  the mapping ability of the convolutional neural network layers in retrieving the all-pairs shortest path of the actors' social relationship,
  and non-linear capability in the deep fully connected layers for movie text sentiments and other social media characteristics.
  The proposed model achieved accuracy of 75\% in the Chinese Movie Box-Office Forecast $2011\sim2015$ dataset, which is higher than Reed \etal's model.

@@

  With the development of social networks, the actors' influence in social media is increasing,
  and the influence of actors' consumption spreads through the social networks,
  and using the long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between the box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of the movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to summarize the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
  as a result, it is 14\% higher in accuracy than Reed \etal~\cite{reed2016learning}'s model.

@@

I collected $1296$ Chinese films released from 2011 to 2015, and their corresponding social media of the key actors, named as Chinese Movie Box-Office Forecast $2011\sim2015$ dataset.
Look at the box-office distribution of the dataset, the box-office forecasts can be seen as a binary classification task.
To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
So for the movies with less than $2.635$ million box-office are classified as A-class, movies with more than $2.635$ million box-office are classified as B-class.
In the dataset division, the data were randomly selected using the $80\%:20\%$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
Using the actors' social network representation, the actor is quantified, that is,
the fusion of social network features, the shortest path characteristics, and the actors' artistic characteristics.
For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
As shown in Figure 1, the model is divided into three parts:

\begin{itemize}
\item The first part is the fully connected layers, its input feature is the film metadata and movie-related Sina Weibo sentiments, in total of 5 dimensions.
\item The second part is the GRU layers, the input feature is the actor social network measurement characteristics and artistic characteristics, the film cast is a long list,
the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
\item The last part is the 5 CNN layers, input from the actors' social network shortest path feature, similarly, the film cast is a long list,
input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimension feature extraction.
\end{itemize}
Finally, these three parts are merged into one layer and then connect to a Softmax layer, and the $L_2$ regularization method is adopted to avoid overfitting.

In summary, randomly choose 10 movies as the test set, as shown in Table (1).
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Reed \etal model, see Table (2), the proposed model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
and in the box-office prediction task, the model can provide more accurate predictions in the market.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Movie& is\_Hit &BoxOffice\\
\hline\hline
72 hours of sword theft & 1 & 108 \\
Ballera's Little Magic Fairy& 1 & 1916\\
It's us. &1& 28\\
Twin Spirits &1& 310\\
The dinner is crazy too& 1& 4381\\
Basement Horror& 0& 704\\
Tartar Oil Flower Romance& 0& 1\\
Breaking five& 0& 1\\
Kidnapping the door dog& 1& 1\\
Beijing Love Story& 1& 40555\\
\hline
\end{tabular}
\end{center}
\caption{The box-office model predictions in movie test dataset of 10 samples.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Reed \etal  & 61.54\% \\
FGC & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on the prediction models.}
\end{table}

@@

According to the box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN prediction model, tested on the Chinese Movie Box-Office Forecast $2011\sim2015$ dataset, the model has accuracy of 75\%, which has improved 14\% compared to Reed \etal's model.
